\section*{Resumen}
El área de Secretaría de Extensión de la \gls{fce} de la \gls{unam} emite certificados
académicos de eventos o actividades efectuados por el sector. Los certificados académicos 
constatan que una persona participó de un curso o evento, también sí lo aprobó.
 En este trabajo de tesis se diseña y desarrolla una propuesta de sistema de validación de documentos digitales  con tecnología Blockchain 
para validar los certificados académicos emitidos por la entidad y respaldar que no fueron alterados. 

Palabras Claves: blockchain, dirección, validación, contrato inteligente, documentos digitales.




\section*{Abstract}
% The Extension Secretariat area of the School of Economics Sciences of the National University of Misiones (UNaM) issue academic
% certificates of events or activities carried out by them. The academic certificates confirm that a person participated of the  course or event, also 
% if  approved it. 
% In this thesis is design and develop for a  proposal of a  digital document  validation system with Blockchain tegnology for validate the academic
% certificates issues for the entity and backup that it haven't been  altered. 

The Extension Secretariat area of the School of Economic Sciences of the National University of Misiones (UNaM) issues academic certificates of events or activities carried out by them. The academic certificates confirm that a person participated in the course or event, also if approved. 
This thesis is to design and develop a  proposal of a  digital document validation system with Blockchain technology to validate the academic certificates issues for the entity and backup that it hasn't been altered.

Keywords: blockchain, address, validation, smart contract,  digital documents.


\newpage
\section*{Dedicatorias}

A mi familia por sus sacrificios, alientos  y acompañamientos aunque a algunos ya no los pueda ver.

A mis directores que me prestaron parte de su tiempo para finalizar este trabajo.

A mis amigos por motivarme a seguir.




